Evaluating Perceptual Judgements on 3D Printed Bar Charts

### 2024-01-22 jds.rmd
Residual plots

mod <- lmer(response ~ (1|subject) + ratio + plot + type,
            data = res)
modsum <- summary(mod)
modaov <- anova(mod)
modaovsum <- summary(modaov)

@@

@@

>>>>

mod <- lmer(response ~ (1|subject) + factor(ratio)+plot+factor(type),
            data = res)
modsum <- summary(mod)
modaov <- anova(mod)
modaovsum <- summary(modaov)

@@

Model diagnostic plots show slight violations of normality with the error term, particularly with right-skewed residuals.
Plots of the data for each ratio tend to suggest that some participants might have tried rounding to the ratio increments of fives and tens. 
For example, participants tended to favor estimating the ratio of 0.562 to around 0.5.
Since linear models are reasonably robust to violations of normality, we will assume that the model reasonably fits.
Plots of the residual diagnostics can be found under the supplemental material in \Cref{fig:residualplots}.

@@

```{r residualplots}
#| fig-width: 3
#| fig-height: 3
#| fig-cap: "Residual diagnostic plots for the linear mixed model."
#| fig-subcap:
#| - Fitted vs. predicted residuals
#| - Q-Q plot
#| out-width: ".49\\linewidth"
#| fig-show: "hold"
#| layout-ncol: 2

r = residuals(mod)
p = predict(mod)

ggplot(mapping = aes(x = p, y = r)) +
  geom_point() + 
  geom_hline(yintercept = 0, linetype = 'dashed', color = 'red') + 
  theme_bw() + 
  labs(x = 'Fitted value',
       y = 'Residual')

ggplot(mapping = aes(sample = r)) + 
  geom_qq() + 
  geom_qq_line(color = 'red', linetype = 'dashed') + 
  theme_bw() + 
  labs(x = 'Theoretical Quantiles',
       y = 'Sample Quantiles')
